### 2018-08-07 paper/security-discussion.tex
rps requirements in security discussion
Adds security of SPORES to discussion

>>>>

Although the requirements on \ac{RPS} of being uniformly randomly
distributed and privacy-preserving are not easily met in practice,
there are some promising candidates~\cite{Octopus, BrahmsRPS}.\name
does not put any other constraints on the \ac{RPS} used.

\paragraph*{Security of \ac{SPORES}}

\Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
the security they provide is as secure as the mixing strategy (or flushing 
algorithm) allows.
Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
the mixing strategy.
Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
messages; it immediately forwards the messages.
This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
vulnerable to traffic analysis than batching 
mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
  probably look for the original papers} --- this vulnerability is inherited 
from the mixing strategy.

\Ac{SPORES} also inherits a vulnerability from random-walk protocols and the 
fact that a large message is split into chunks.
Since the chunks can take several paths from source to destination, the source 
will send and the destination will receive more traffic than other nodes in the 
network~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
  probably look for the original papers}.
However, this is slightly alleviated by the fact that the source and 
destination can be several different devices --- \ie from the \squad{}s.
